\section{Requirements}
\label{chapter6}

“System” refers only to the ACC.

\subsection{Safety related requirements}




 \begin{enumerate}[label*=\arabic*.]
 	\item \label{req.1}  Requirement: \\
	 	The system shall be able to respond to a measurement error within 1 second by deactivating itself.  \\
	 	%Folge Requirements: \ref{req.1.1} , \ref{req.1.2}  
	 	%\begin{enumerate}[label*=\arabic*.]
	 		%\item \label{req.1.1}  Requirement  \\
	 		%At program start the LED indicating an error must be tested.\ref{req.2}\\ 
	 		%\item \label{req.1.2} Requirement   \\
	 		%At program start the USART sending error messages must be tested.\\ 
	 	%\end{enumerate}

        \item \label{req.2} Requirement: \\
        The system shall automatically detect sensor failure by checking the measured values for plausibility.  \\
	 	\item \label{req.3} Requirement: \\
        The system shall inform the driver of a detected sensor failure by means of a red LED indicator on the display. \\
        \item \label{req.4} Requirement: \\
        The system shall switch off when a sensor failure is detected. \\
        \item \label{req.5} Requirement: \\
        The system shall automatically detect a failure of the communication subsystem (Bluetooth) by recognizing that a packet could not be sent, or by recognizing that no response is received within a defined period (500 ms) after a successful transmission. \\
        \item \label{req.6} Requirement: \\
        The system is designed to inform the driver of a detected communication subsystem failure by switching on a red warning LED. \\
        \item \label{req.7} Requirement: \\
        The system shall automatically switch off when a communication subsystem (Bluetooth) error is detected. \\
        \item \label{req.8} Requirement: \\
        If a failure of the communication subsystem (Bluetooth) is detected, the system shall initiate a connection. \\
        \item \label{req.9} Requirement: \\
        The system shall inform the driver about the status of the system via a green status LED and the ACC push button display (ACC ON/ACC OFF). \\
        \item \label{req.10} Requirement: \\
        The system shall not be activated if the sensors or communication have failed. \\
        \item \label{req.11} Requirement: \\
        Once activated, the system shall note the current speed of the vehicle and not exceed it. \\
        \item \label{req.12} Requirement: \\
        The system shall deactivate when the vehicle speed falls below 30 km/h. \\
        \item \label{req.13} Requirement: \\
        The system shall reduce the speed to n/2 km/h at a measured distance of n meters. \\
	 \end{enumerate}

%Das System soll innerhalb 1 sek auf einen Fehler in der Messung reagieren können indem es sich deaktiviert.

%Das System soll einen Ausfall der Sensoren selbstständig erkennen indem es die Messwerte auf Plausibilität überprüft.

%Das System soll bei einem erkannten Sensorausfall den Fahrer durch eine Rote LED-Anzeige am Display informieren.

%Das System soll sich bei einem erkannten Sensorausfall ausschalten.

%Das System soll einen Ausfall des Kommunikationssubsystems (Bluetooth) automatisch erkennen indem es erkennt, dass ein Paket nicht versandt werden konnte, oder indem es erkennt das nach einem erfolgreichen Senden keine Antwort innerhalb eines definierten Zeitraums (10ms) bekommt.

%Das System soll bei einem erkannten Kommunikationssubsystemausfall den Fahrer durch das einschalten einer Roten Warn-LED informieren.

%Das System soll sich bei einem erkannten Kommunikationssubsystems (Bluetooth) -Fehler automatisch ausschalten.

%Bei einem erkannten Ausfall des Kommunikationssubsystems (Bluetooth) soll das System einen Verbindungsaufbau starten.

%Das System soll den Fahrer über den Zustand des Systems informieren durch eine Grüne Status-LED und durch die ACC Push Button darstellung (ACC ON/ACC OFF).

%Das System soll sich nicht Aktivieren lassen wenn die Sensoren oder die Kommunikation ausgefallen sind.

%Das System soll sobald es aktiviert wird, die derzeitige geschwindigkeit des Fahrzeugs merken und nicht überschreiten.

%Das System soll sich bei einer Unterschreitung der Fahrzeuggeschwindigkeit von 30 km/h deaktivieren.

%Das System soll bei einem gemessenen Abstand von n Metern, die Geschwindigkeit auf n/2 km/h runterregeln.




        
	 	

\subsection{Security related requirements}


\subsection{Requirements with no influence on Safety and Security}

\begin{enumerate}[label*=\arabic*.]
 	\item \label{req.1}  Requirement: \\
	 	The ACC display shall have a black background.  \\
	 	%Folge Requirements: \ref{req.1.1} , \ref{req.1.2}  
	 	%\begin{enumerate}[label*=\arabic*.]
	 		%\item \label{req.1.1}  Requirement  \\
	 		%At program start the LED indicating an error must be tested.\ref{req.2}\\ 
	 		%\item \label{req.1.2} Requirement   \\
	 		%At program start the USART sending error messages must be tested.\\ 
	 	%\end{enumerate}

        \item \label{req.2} Requirement: \\
        The speed shall be displayed in km/h.  \\
	 	\item \label{req.3} Requirement: \\
        The distance to the vehicle in front shall be displayed in meters. \\
        \item \label{req.4} Requirement: \\
        The speed shall be displayed as an integer value without decimal places. \\
        %The ESC key shall close the GUI window. \\
        \item \label{req.5} Requirement: \\
        There shall be one button for acceleration and one for deceleration in the GUI. \\
        \item \label{req.6} Requirement: \\
        The GUI shall allow the speed to be continuously increased or decreased by holding down the acceleration and deceleration buttons without the user having to tap repeatedly. \\

        
	 \end{enumerate}

